Attack-Tolerant Networks: A Structural, Multipath Approach

### 2016-08-07 wsdm-2017/source/paper.tex
Revise algorithm and discussion.

Using the partial trust model, we are able to reduce complex networks to
simply a number of redundant, independent paths.
This reduction enables the application of standard error detection techniques
\cite{avizienis_basic_2004, von_neumann_probabilistic_1956},
which rely on independent errors.
While adversarial faults along a single path are correlated,
faults in independent paths are not.
Thus fault tolerance techniques can be applied,
even in the presence of adversarial errors,
when messages are sent in parallel,
a technique known as {\em concurrent multipath routing}
\cite{zin_survey_2015, qadir_exploiting_2015}.
The receiver can then use the redundant messages to detect and/or correct
errors.
Using the partial trust model, we formally evaluate the 
effects of network structure on attack-resistance and show that the probability
of undetected errors decreases exponentially with the number of
independent paths between source and destination,
even when no individual path is entirely trusted.

@@

@@

@@

We now specify the multipath routing scheme and prove
that provides $2^h$ disjoint paths between
the $h$-hop trusted neighborhoods of any two nodes in an $m$-bit
wrap-around butterfly network.
Utilizing vertex transitivity, we label the source node as
$(l^{(0)}, z^{(0)}) = (0, 0)$ and denote the destination node as $w = (l_w, z_w)$,
without loss of generality.

Let $s$ be an $h$-bit binary string with $s_i$ denoting the bit at index $i$.
There are $2^h$ such strings.
Let $v_s^{(t)} = (l^{(t)}, z^{(t)})$ be the node at position $t$
in the path parameterized by $s$.
For convenience,
we will omit the subscript $s$ when it is obvious from context.
We define three distinct partitions of $m$-bit binary strings.
Let $Q_{v^{(0)}}$ ($\overline{Q_{v^{(0)}}}$) be the set of $m$-bit
strings in which the bits at
all indeces $h \leq i < l_w - h$ match (do not all match) those of $z^{(0)}$.
Note that $Q_{v^{(0)}}$ is trivially all $m$-bit strings if $l_w < 2h$.
Let $R_s$ ($\overline{R_s}$) be the set of $m$-bit strings with the lowest $h$
bits all matching (not all matching) the bits of $s$.
Let $S_s$ ($\overline{S_s}$) be the set of $m$-bit strings with the $h$ bits
preceeding index $l_w$ all matching (not all matching) the bits of $\tilde{s}$,
where $\tilde{s}$ is a cyclic permutation of $s$ defined below.
\beq
Q_{v^{(0)}} &=&
\{z \in \mathbb{Z}_2^m \mid \;
\neg \exists i \in \mathbb{Z} : h \leq (i < l_w - h) \land z_i \neq z_i^{(0)} \}
\\
\overline{Q_{v^{(0)}}} &=& \mathbb{Z}_2^m \setminus Q_{v^{(0)}}
\\
R_s &=&
\{z \in \mathbb{Z}_{2}^m \mid \;
\forall i \in \mathbb{Z}_2^h z_i = s_i \}
\\
\overline{R_s} &=& \mathbb{Z}_2^m \setminus R_s
\\
S_s &=&
\{z \in \mathbb{Z}_{2}^m \mid \;
\forall i \in \mathbb{Z}_2^h z_{(l_w - h + i)} = \tilde{s}_i \}
\\
\overline{S_s} &=& \mathbb{Z}_2^m \setminus S_s
\\
\tilde{s}_i &=& s_{(i + l_w) \text{ mod } h}.
\eeq
We will make use of the fact that:
\beq
s \neq s^\prime &\implies&
S_s \cap S_{s^\prime} = R_s \cap R_{s^\prime} = \emptyset.
\eeq

@@

While decentralized architectures have recieved much attention,
methods for classifying, and evaluating decentralization
are in their infancy.
The trust model and multipath fault tolerance technique proposed in this
paper provide a practical fault tolerance architecture for applications when
network structure can be imposed,
as well as a more general method for evaluating the role of network structure
on fault tolerance.

Fault-tolerant network infrastructures have many direct applications.
Areas such as cryptocurrency, secure multiparty computation, and wireless
sensor networks have immediate need for scalable, fault-tolerant
infrastructures.
Many Internet services---email, social networks, cloud storage---are still
highly centralized and vulnearble to technical and non-technical attacks.
Decentralized fault tolerance is one approach to securing these important
services and making networked communication safer.

While the primary purpose of our proposed fault tolerance technique is the
threat of message blocking or corruption, it can provide some improvements
to secrecy and privacy.
For example, if a message is broken into parts and each part is sent along
a different random subset of routes, an attacker who succesfully compromises
one part of the message will still be unable to compromise the rest.

While {\em confidentiality} is a common concern in secure communication,
it is not the focus of this paper.
Existing cryptographic techniques for confidentiality are relatively
mature compared to those for tolerating censorship.
In fact, an attacker might use targeted attacks to achieve censorship
as a fallback when surveillance isn't feasible.
However, we stress that the technqiues presented in this paper
are entirely compatible with, and in some cases could enhance, existing
privacy and secrecy techniques.
For example, the well-known {\em man-in-the-middle} attack exploits a privileged
network position to attack otherwise secure cryptography,
suggesting that structural approaches can complement cryptographic ones.

Our present contributions are limited in several ways.
The partial trust model, while making fewer assumptions than web of trust
approaches, still depends on some transitivity of trust,
which may be a questionable assumption in many cases.
Better trust models are still needed.

The primary limitation of our structured network approach is that
link structure is imposed rather than self-organized.
This requirement may be appropriate for appliations such as
wireless sensor networks,
or slow-changing institutional infrastructure,
in which the architect has considerable control over link structure.
But in general, it remains an open question whether self-organized networks
can be restructured, or buit from the ground up in such a way that
structured multipath fault tolerance technqiues can be applied.
Similarly, structured network topologies such as the butterfly are defined
only for specific values.
Although these values can be as large as desired,
how to apply methods such as ours to networks with an intermediate number
of nodes remains an open question.

>>>>

Using the partial trust model, we are able to reduce complex networks to
simply a number of redundant, independent paths.
This reduction enables the application of standard error detection techniques
\cite{avizienis_basic_2004, von_neumann_probabilistic_1956},
which rely on independent errors.
While adversarial faults along a single path are correlated,
faults in independent paths are not.
Thus fault tolerance techniques can be applied,
even in the presence of adversarial errors,
when messages are sent in parallel,
a technique known as {\em concurrent multipath routing}
\cite{zin_survey_2015, qadir_exploiting_2015, khiani_comparative_2013}.
The receiver can then use the redundant messages to detect and/or correct
errors.
Using the partial trust model, we formally evaluate the 
effects of network structure on attack-resistance and show that the probability
of undetected errors decreases exponentially with the number of
independent paths between source and destination,
even when no individual path is entirely trusted.

@@

We now present a routing algorithm to construct multiple independent paths
between two nodes in a butterfly network.
Independence requires that routes between two nodes $v$ and $w$ have no nodes
in common, unless those nodes are less than distance $h$ from either $v$ or $w$.
Informally, the algorithm achieves this by using the first $h$ hops to
reach as many distinct nodes as possible,
then routing from each of those to a distinct intermediary node,
and finally routing from the intermediary to the destination.
By ensuring that the place-within-level differs for all paths
(outside of the trusted neighborhoods of $v$ and $w$)
the algorithm guarnatees independence.
As with the unipath routing algorithm,
each of the multiple paths proceed using down and down-right edges,
cycling through levels one at a time.
However, we cycle through the levels twice, once to route from $v$ to a
particular path's intermediary node,
and again to route from the intermediary to $w$.
In the first cycle, path independence is guaranteed by ensuring that
all paths differ in the first $h$ bits of the place-within-level.
Similarly, in the second cycle,
independence is guaranteed by ensuring that all paths differ in the
$h$ bits of the place-within-level preceeding the destination index
(see Figure \ref{fig:route-overview}).

@@

                outer sep=0pt, on chain, double},

@@

We now formally specify the multipath routing scheme and prove
that provides $2^h$ disjoint paths between
the $h$-hop trusted neighborhoods of any two nodes in an $m$-bit
wrap-around butterfly network.
Utilizing vertex transitivity, we label the source node as
$(l^{(0)}, z^{(0)}) = (0, 0)$ and denote the destination node as $w = (l_w, z_w)$,
without loss of generality.

Let $s$ be an $h$-bit binary string with $s_i$ denoting the bit at index $i$.
There are $2^h$ such strings.
Let $v_s^{(t)} = (l^{(t)}, z^{(t)})$ be the node at position $t$
in the path parameterized by $s$.
For convenience,
we will omit the subscript $s$ when it is obvious from context.
We define three distinct partitions of $m$-bit binary strings.
Let $Q_{v^{(0)}}$ ($\overline{Q_{v^{(0)}}}$) be the set of $m$-bit
strings in which the bits at
all indeces $h \leq i < l_w - h$ match (do not all match) those of $z^{(0)}$.
Note that $Q_{v^{(0)}}$ is trivially all $m$-bit strings if $l_w < 2h$.
Let $R_s$ ($\overline{R_s}$) be the set of $m$-bit strings with the lowest $h$
bits all matching (not all matching) the bits of $s$.
Let $S_s$ ($\overline{S_s}$) be the set of $m$-bit strings with the $h$ bits
preceeding index $l_w$ all matching (not all matching) the bits of $\tilde{s}$,
where $\tilde{s}$ is a cyclic permutation of $s$:
\beq
\tilde{s}_i &=& s_{(i + l_w) \text{ mod } h}.
\eeq
We will make use of the fact that:
\beq
s \neq s^\prime &\implies&
S_s \cap S_{s^\prime} = R_s \cap R_{s^\prime} = \emptyset.
\eeq

@@

While decentralized protocols have received much attention for their potential
fault tolerance applications,
a better understanding of how network structure contributes to fault tolerance
is necessary.
We have proposed a number of contributions towards this understanding:
a {\em partial trust model} for quantifying the effective redundancy
of a network,
a {\em multipath fault tolerance} scheme for using that redundancy to detect
errors,
and a {\em concurrent multipath routing} algorithm enabling this scheme to
be implemented on the butterfly network.

Fault-tolerant network infrastructures have many direct applications.
Areas such as cryptocurrency
\cite{mazieres_stellar_2015,nakamoto_bitcoin:_2008,king_ppcoin:_2012},
secure multiparty computation
\cite{yao_protocols_1982,chaum_multiparty_1988,goldreich_how_1987},
and wireless sensor networks
\cite{khiani_comparative_2013}
have immediate need for scalable, fault-tolerant infrastructures.
Many Internet services (e.g., email, social networks, cloud storage)
are still highly centralized and vulnearble to technical and
non-technical (i.e. coercive) attacks.
Fault tolerance using {\em both} decentralized protocols and
decentralized network structures
is one approach to securing these important
services and making networked communication safer.

We have also focused specifically on adversarial faults that block or
change messages (e.g., censorship).
We have not specifically addressed {\em confidentiality}:
how to keep those messages private.
Existing cryptographic techniques for confidentiality are relatively
mature compared to those for tolerating censorship.
In fact, an attacker might use targeted attacks to achieve censorship
as a fallback when surveillance isn't feasible.
However, the technqiues presented in this paper
are entirely compatible with, and in some cases could enhance, existing
confidentiality techniques.
For example, the well-known {\em man-in-the-middle} attack exploits a privileged
network position to attack otherwise secure cryptography,
suggesting that structural approaches can complement cryptographic ones.

Our multipath fault tolerance scheme can be applied to any network
that has both sufficient redundancy and a routing algorithm
that maps local links to independent network paths.
These requirements make the approach well-suited for structured networks,
in which link structure can be dictated,
such as the butterfy.
While the ability to control network topology is only achievable in some
applications, those applications are nonetheless significant
(e.g. overlay networks \cite{lua_survey_2005, korzun_structured_2013},
formal organizations \cite{mohr_explaining_1982},
government-regulated cellular networks \cite{walker_mass_2012},
and call tree notification systems \cite{nickerson_thinking_2010}).
Furthermore, when high levels of adversarial fault tolerance are required,
new socio-technical systems might choose to incorporate such networks.
For example,
a coallition of groups supporting free expression could use our results
to construct a censorship-resistant communication network
by cultivating the necessary trust relationships.
In the general case,
while the partial trust model can be applied to unstructured networks,
additional work is needed to identify how to ensure redundancy and
identify independent paths in unstructured networks.
